\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading{SteamVault | \textit{Python, FastAPI, PostgreSQL, Supabase, Render, Cron Jobs}}{https://github.com/imrahnf/steam-vault}
        \resumeItemListStart
        \resumeItem{Built a modular backend system to automatically track Steam activity and generate daily snapshots, summaries, and insights, enabling historical analysis beyond Steam's default static playtime view.}
        \resumeItem{Implemented a production-ready FastAPI architecture with Supabase PostgreSQL and a custom caching layer, reducing redundant Steam API calls and improving response performance across all analytics endpoints.}
        \resumeItem{Developed comprehensive analytics modules including 14-day trend calculations, activity heatmaps, multi-game comparisons, and streak detection, providing transparent and interpretable metrics for user activity patterns.}
        \resumeItem{Built secure admin-protected routes and scheduled cron workflows (Google Cloud Scheduler) to automate fetch cycles, daily summary generation, and uptime pings for reliable long-running operation.}
        \resumeItem{Designed a demo mode using a separate database to safely showcase analytics without exposing real Steam data.}

    \resumeItemListEnd

  \resumeProjectHeading{SafeCord | \textit{Python, FastAPI, NLP, SQLite}}{https://github.com/imrahnf/Safecord}
    \resumeItemListStart
      \resumeItem{Developed an AI-powered moderation bot to detect and flag potential grooming or unsafe user behavior using zero-shot classification models, enabling proactive safety insights across Discord servers.}
      \resumeItem{Designed and implemented manual flagging, watchlist, and log management commands, allowing moderators to track user risk patterns beyond offensive keyword triggers.}
      \resumeItem{Built a FastAPI backend with SQLite database for secure storage of moderation logs and NLP confidence scores, supporting traceability and cross-session risk analysis.}
      \resumeItem{Developed Jupyter Notebook to visualize behavior patterns via boxplots, heatmaps, and score distributions, showcasing potential for data-driven safety dashboards.}
    \resumeItemListEnd
    
    \resumeProjectHeading{Breast Cancer Detection Model Comparison | \textit{Python, Weka, Excel}}{https://github.com/imrahnf/breast-cancer-ml-comparison}
  \resumeItemListStart
    \resumeItem{Conducted comparative analysis of Decision Tree (J48) and Neural Network (MLP) models on the Weka Breast Cancer dataset, running 30 randomized trials to ensure statistically reliable results.}
    \resumeItem{Built custom t-distribution visualization in Python (NumPy, SciPy, Matplotlib) to interpret rejection regions, improving clarity of model evaluation for academic reporting.}
    \resumeItem{Delivered a comprehensive research report with reproducible code and visualizations, demonstrating Decision Tree accuracy of 70.1\% vs. Neural Network at 65.4\%, supporting model reliability in early cancer detection.}
    
  \resumeItemListEnd
    \resumeProjectHeading{Personal Website | \textit{Astro}}{https://www.omrahnfaqiri.com/}
      \resumeItemListStart
        \resumeItem{Developed \& deployed personal portfolio with automated CI/CD pipeline on Netlify to showcase projects and skills.}
      \resumeItemListEnd


\resumeSubHeadingListEnd
